Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-05-24 automatica/automatica.tex
added paper title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added authors and affiliations
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\title{In Catilinam IV\thanksref{footnoteinfo}} % Title, preferably not more 
                                                % than 10 words.

\thanks[footnoteinfo]{This paper was not presented at any IFAC 
meeting. Corresponding author M.~T.~Cicero. Tel. +XXXIX-VI-mmmxxi. 
Fax +XXXIX-VI-mmmxxv.}

\author[Paestum]{Marcus Tullius Cicero}\ead{cicero@senate.ir},    % Add the 
\author[Rome]{Julius Caesar}\ead{julius@caesar.ir},               % e-mail address 
\author[Baiae]{Publius Maro Vergilius}\ead{vergilius@culture.ir}  % (ead) as shown

\address[Paestum]{Buckingham Palace, Paestum}  % Please supply                                              
\address[Rome]{Senate House, Rome}             % full addresses
\address[Baiae]{The White House, Baiae}        % here.

>>>>

%\thanksref{footnoteinfo}

\title{Safe and Robust Formal  Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications} % Title, preferably not more 
                                                % than 10 words.

%\thanks[footnoteinfo]{This paper was not presented at any IFAC 
%meeting. Corresponding author M.~T.~Cicero. Tel. +XXXIX-VI-mmmxxi. 
%Fax +XXXIX-VI-mmmxxv.}

\author[abate]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
\author[bessa]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
\author[cattaruzza]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
\author[cordeiro]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
\author[david]{Cristina David}\ead{cristina.david@cs.ox.ac.uk},
\author[kesseli]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
\author[kroening]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
\author[polgreen]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}

\address[abate]{University of Oxford, UK}
\address[bessa]{Federal University of Amazonas, Brazil}
\address[cattaruzza]{University of Oxford, UK}
\address[cordeiro]{University of Oxford, UK}
\address[david]{University of Oxford, UK}
\address[kesseli]{University of Oxford, UK}
\address[kroening]{University of Oxford, UK}
\address[polgreen]{University of Oxford, UK}

%\author[Paestum]{Marcus Tullius Cicero}\ead{cicero@senate.ir},    % Add the 
%\author[Rome]{Julius Caesar}\ead{julius@caesar.ir},               % e-mail address 
%\author[Baiae]{Publius Maro Vergilius}\ead{vergilius@culture.ir}  % (ead) as shown

%\address[Paestum]{Buckingham Palace, Paestum}  % Please supply                                              
%\address[Rome]{Senate House, Rome}             % full addresses
%\address[Baiae]{The White House, Baiae}        % here.
